### 2016-01-18 papers/CAFe/HIPS-paper/multigrid.tex
Near final pass.

The multigrid algorithm uses a series of successively coarser grids to
iteratively approximate the solution obtained from the preceding
finer grid.  Higher frequency error modes are damped out as the
solution processes up the grid hierarchy.  At the top of the
hierarchy, an exact solution is obtained and then this solution is
iterated and propagated down the grid hierarchy form coarser to finer
grids.  After a few sweeps up and down the hierarchy the solution with
have been obtained on the desired original grid.

@@

Two levels of the grid hierarchy are shown in \ref{fig_grids} running on a processor computing on
an interior portion of the grid; additional images are computing on regions to the left and right of
the region shown in the figure.  The finest grid (size N) is shown
in the bottom of the figure with cell indices running from (-1:N+1).  Cells 0 and N are shared
between image neighbors to the left and right (indicated by the light blue coloring and the vertical
dashed lines).  These shared cells are computed redundantly on each program image.

@@

The second grid level N/2 is also shown in Figure \ref{fig_grids}.  Data on this grid is obtained
by simple interpolation from information on grid level N as shown in Figure \ref{fig_restric}.
We call this interpolation a restriction and refer the reader to previous work on the multigrid
technique for more information\cite{multigrid_methods}.  The approximate solution on the N/2
grid is relaxed a few times and then passed on the grid level N/4 for further iteration.

@@

The multigrid algorithm has been implemented in Fortran using the CAFe
syntax described in the previous section. Data coarrays at each grid
level are declared, allocated, and initialized on each program image.
These coarrays are then copied to the subimages by the parent, hosting
images.  Below we show the implementation of the relaxation loop on
grid level N.  Each iteration step incorporates concurrent computation
on an image and its hosted subimage.  In order to execute
concurrently, we must declare a event variable to allow concurrent
execution and then synchronization once \emph{both} computation and
the subimage \emph{and} the image have completed.

The event variable is declared as,
\small
\begin{verbatim}
 type(event_type) :: evt
\end{verbatim}
\normalsize
After initialization, this event variable has its count variable set to 0 and is incremented
each time the subimage task completes during an iteration of the code segment shown below:
\small
\begin{verbatim}
 do i = 1, nsteps                            1
   call relax (N, V1h[dev], Buf[dev])        &
                    [[dev, EVENT=evt]]       2
   call relax_boundary (N, V1h)              3

@@

Most of the computation is accomplished by the subimage executing the \texttt{relax}
procedure (not shown) operating over the interior corresponding to fine grid indices (1:N-1).
Concurrently, \texttt{relax\_boundary} operates on the boundary indices 0 and N
(note that memory for the boundary computation in located on local image as
the coarray \texttt{V1h} is not coindexed using square bracket notation in statement 3.

>>>>

The multigrid algorithm uses a series of successively coarser grids to
iteratively approximate the solution obtained from the preceding
finer grid.  Higher frequency error modes are damped out as the
solution processes up the grid hierarchy.  At the top of the
hierarchy, an exact solution is obtained and then this solution is
iterated and propagated down the grid hierarchy form coarser to finer
grids.  After a few sweeps up and down the hierarchy the solution will
have been obtained on the desired original grid.

@@

Two levels of the grid hierarchy are shown in Fig. \ref{fig_grids} running on a processor computing on
an interior portion of the grid; additional images are computing on regions to the left and right of
the region shown in the figure.  The finest grid (size N) is shown
in the bottom of the figure with cell indices running from (-1:N+1).  Cells 0 and N are shared
between image neighbors to the left and right (indicated by the light blue coloring and the vertical
dashed lines).  These shared cells are computed redundantly on each program image.

@@

The second grid level N/2 is also shown in Figure \ref{fig_grids}.  Data on this grid is obtained
by simple interpolation from information on grid level N as shown in Figure \ref{fig_restric}.
We call this interpolation a restriction and refer the reader to previous work on the multigrid
technique for more information\cite{multigrid_methods}.  The approximate solution on the N/2
grid is relaxed a few times and then passed on to grid level N/4 for further iteration.

@@

The multigrid algorithm has been implemented in Fortran using the CAFe
syntax described in the previous section. Data coarrays at each grid
level are declared, allocated, and initialized on each program image.
These coarrays are then copied to the subimages by the parent, hosting
images.  Below we show the implementation of the relaxation loop on
grid level N.  Each iteration step incorporates concurrent computation
on an image and its hosted subimage.  In order to execute
concurrently, we must declare an event variable to allow concurrent
execution and then synchronization once computation on \emph{both} 
the subimage \emph{and} the image have completed.

The event variable is declared as,
%%\small
\begin{verbatim}
 type(event_type) :: evt
\end{verbatim}
%%\normalsize
After initialization, this event variable has its count variable set to 0 and is incremented
each time the subimage task completes during an iteration of the code segment shown below:
\small
\begin{verbatim}
 do i = 1, nsteps                            1
   call relax (N, V1h[dev], Buf[dev])        &
                    [[dev, EVENT=evt]]       2
   call relax_boundary (N, V1h)              3

@@

Most of the computation is accomplished by the subimage executing the \texttt{relax}
procedure (not shown) operating over the interior corresponding to fine grid indices (1:N-1).
Concurrently, \texttt{relax\_boundary} operates on the boundary indices 0 and N
(note that memory for the boundary computation is located on local image as
the coarray \texttt{V1h} is not coindexed using square bracket notation in statement 3.
